### 2021-08-13 paper/paper.tex
Remove erroneous plural "s"
Fix typo

Since Julia uses a serial just-ahead-of-time compiler that currently does not cache
code between different Julia sessions, the initial compilation time can be
annoying. For example, the time to finish a first \trixi simulation in a fresh Julia
session and plot the results on a notebook can take between 30 seconds and a
minute. Having compiled the code, the second simulation and plot takes less than
0.05 seconds. Thus, switching to Julia requires adapting the workflow compared
to other languages such as keeping a REPL session active for a longer time and
using packages such as Revise.jl\footnote{\url{https://github.com/timholy/Revise.jl}}.
This is particularly problematic in HPC environments. There are tools such as
PackageCompiler.jl\footnote{\url{https://github.com/JuliaLang/PackageCompiler.jl}}
that can help with these tasks but a good workflow usable for development and
deployment still has to be found.

@@

While Julia offers its own approach to distributed computing via the \lstinline{Distributed} package
in the standard library, its performance and scalability are currently limited \cite{byrne2021mpi}.
As an alternatively, the package MPI.jl utilizes the Message Passing Interface (MPI) for data
exchange \cite{byrne2021mpi}. It provides an API similar to MPI's C interface and allows to either
wrap MPI binaries installed through Julia's package manager or to make use of an existing MPI
installation.  Most Julia projects focusing on distributed-memory simulations seem to be using
MPI.jl, such as ClimateMachine.jl\footnote{\url{https://github.com/CliMA/ClimateMachine.jl}} or
ImplicitGlobalGrid.jl\footnote{\url{https://github.com/eth-cscs/ImplicitGlobalGrid.jl}}.  In
general, the performance of MPI programs written in Julia is comparable to C programs
\cite{hunold2020benchmarking}, and parallel simulations with Julia have been shown to scale
to more than 5{,}000 GPUs with MPI.jl \cite{omlin2020solving}.

>>>>

Since Julia uses a serial just-ahead-of-time compiler that currently does not cache
code between different Julia sessions, the initial compilation time can be
annoying. For example, the time to finish a first \trixi simulation in a fresh Julia
session and plot the results on a notebook can take between 30 seconds and a
minute. Having compiled the code, the second simulation and plot take less than
0.05 seconds. Thus, switching to Julia requires adapting the workflow compared
to other languages such as keeping a REPL session active for a longer time and
using packages such as Revise.jl\footnote{\url{https://github.com/timholy/Revise.jl}}.
This is particularly problematic in HPC environments. There are tools such as
PackageCompiler.jl\footnote{\url{https://github.com/JuliaLang/PackageCompiler.jl}}
that can help with these tasks but a good workflow usable for development and
deployment still has to be found.

@@

While Julia offers its own approach to distributed computing via the \lstinline{Distributed} package
in the standard library, its performance and scalability are currently limited \cite{byrne2021mpi}.
As an alternative, the package MPI.jl utilizes the Message Passing Interface (MPI) for data
exchange \cite{byrne2021mpi}. It provides an API similar to MPI's C interface and allows to either
wrap MPI binaries installed through Julia's package manager or to make use of an existing MPI
installation.  Most Julia projects focusing on distributed-memory simulations seem to be using
MPI.jl, such as ClimateMachine.jl\footnote{\url{https://github.com/CliMA/ClimateMachine.jl}} or
ImplicitGlobalGrid.jl\footnote{\url{https://github.com/eth-cscs/ImplicitGlobalGrid.jl}}.  In
general, the performance of MPI programs written in Julia is comparable to C programs
\cite{hunold2020benchmarking}, and parallel simulations with Julia have been shown to scale
to more than 5{,}000 GPUs with MPI.jl \cite{omlin2020solving}.
